### 2014-03-19 Docs/flowchart/flowchart.tex
put the notation parts from the multilevel paper here and also put in the delta_gamma1_term stuff from paper III

\subsection{Volume Discrepancy Changes}
\begin{itemize}
\item In {\bf Step 2B}, to compute $w_0$, we need to account for the volume discrepancy
term by computing $p_{\rm EOS} = \overline{p(\rho,h,X_k)^n}$.
\item In {\bf Step 3}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left\{ \left(S^{\nph,\star\star} - \overline{S^{\nph,\star\star}}\right)
+ \frac{f}{\gammabar^n p_0^n}
\left[\frac{p(\rho,h,X_k)^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n}\right]\right\}.
\end{equation}
\item In {\bf Step 6B}, to compute $w_0$, we need to account for the volume discrepancy
term by computing $p_{\rm EOS} = \left[\overline{p(\rho,h,X_k)^n} + \overline{p(\rho,h,X_k)^{n+1,\star}}\right]/2$.
\item In {\bf Step 7}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph,\star} \uadvtwo\right) = \beta_0^{\nph,\star}\left\{\left(S^{\nph,\star} - \overline{S^{\nph,\star}}\right) + \frac{f}{\overline{\Gamma_1^{\nph,\star}} p_0^{\nph,\star}} \left[\frac{p(\rho,h,X_k)^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right]\right\},
\end{equation}
where $p(\rho,h,X_k)^{\nph,\star} = \left[p(\rho,h,X_k)^n +p(\rho,h,X_k)^{n+1,\star}\right]/2$.
\item In {\bf Step 11}, the approximate projection should account for the volume
discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph} \Ubt^{n+1} \right)  = \beta_0^{\nph}\left\{  \left(S^{n+1} - \overline{S^{n+1}} \right)
+ \frac{f}{\overline{\Gamma_1^{n+1}} p_0^{n+1}}
\left[\frac{p(\rho,h,X_k)^{n+1} - \overline{p(\rho,h,X_k)^{n+1}}}{\Delta t^n}\right]\right\}.
\end{equation}
\end{itemize}
\subsection{Thermal Diffusion Changes}
Immediately after {\bf Step 4H}, diffuse the enthalpy through 
a time interval of $\dt$.  First, define $(\rho h)^{(1a),\star} = (\rho h)^{(2),\star}$.  
We recompute $(\rho h)^{(2),\star}$ to account for thermal diffusion.  Here we begin
with the enthalpy equation, but consider only the 
diffusion terms,
\begin{equation}
\frac{\partial (\rho h)}{\partial t} = \nabla\cdot\kth\nabla T.
  \end{equation}
We can recast this as an enthalpy-diffusion equation by applying the
chain-rule to $h(p_0,T,X_k)$,
\begin{equation}
\nabla h = h_p \nabla p_0 + c_p \nabla T + \sum_k \xi_k \nabla X_k \enskip ,
\end{equation}
giving
\begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = 
 \nabla\cdot \frac{\kth}{c_p}\nabla h -  
 \sum_k \nabla\cdot \frac{\xi_k \kth}{c_p}\nabla X_k -
 \nabla\cdot \frac{h_p \kth}{c_p}\nabla p_0.
  \end{equation}
Compute $\kth^{(1)}, c_p^{(1)}$, and $\xi_k^{(1)}$ from $\rho^{(1)}, T^{(1)}$, and $X_k^{(1)}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(2),\star} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2),\star}$,
\begin{eqnarray}
\left(\rho^{(2),\star} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla\right)h^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}

>>>>

\subsection{Volume Discrepancy Changes}
\begin{itemize}
\item In {\bf Step 2B}, to compute $w_0$, we need to account for the volume discrepancy
term by computing $p_{\rm EOS} = \overline{p(\rho,h,X_k)^n}$.
\item In {\bf Step 3}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left\{ \left(S^{\nph,\star\star} - \overline{S^{\nph,\star\star}}\right)
+ \frac{f}{\gammabar^n p_0^n}
\left[\frac{p(\rho,h,X_k)^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n}\right]\right\}.
\end{equation}
\item In {\bf Step 6B}, to compute $w_0$, we need to account for the volume discrepancy
term by computing $p_{\rm EOS} = \left[\overline{p(\rho,h,X_k)^n} + \overline{p(\rho,h,X_k)^{n+1,\star}}\right]/2$.
\item In {\bf Step 7}, the MAC projection should account for the volume discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph,\star} \uadvtwo\right) = \beta_0^{\nph,\star}\left\{\left(S^{\nph,\star} - \overline{S^{\nph,\star}}\right) + \frac{f}{\overline{\Gamma_1^{\nph,\star}} p_0^{\nph,\star}} \left[\frac{p(\rho,h,X_k)^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right]\right\},
\end{equation}
where $p(\rho,h,X_k)^{\nph,\star} = \left[p(\rho,h,X_k)^n +p(\rho,h,X_k)^{n+1,\star}\right]/2$.
\item In {\bf Step 11}, the approximate projection should account for the volume
discrepancy term:
\begin{equation}
\nabla \cdot \left(\beta_0^{\nph} \Ubt^{n+1} \right)  = \beta_0^{\nph}\left\{  \left(S^{n+1} - \overline{S^{n+1}} \right)
+ \frac{f}{\overline{\Gamma_1^{n+1}} p_0^{n+1}}
\left[\frac{p(\rho,h,X_k)^{n+1} - \overline{p(\rho,h,X_k)^{n+1}}}{\Delta t^n}\right]\right\}.
\end{equation}
\end{itemize}

\subsection{$\Gamma_1$ Variation Changes}

The constraint we derive from requiring the pressure to be close to the background hydrostatic
pressure takes the form:
\begin{equation}
\nablab \cdotb \Ub + \frac{1}{\Gamma_1 p_0} \frac{Dp_0}{Dt} = S \enskip .
\end{equation}
The default \maestro\ algorithm replaces $\Gamma_1$ with $\gammabar$, allowing us
to write this as a divergence constraint.  In paper~III, we explored the effects of
localized variations in $\Gamma_1$ by writing $\Gamma_1 = \gammabar + \delta \Gamma_1$.
This gives us:
\begin{equation}
\nablab \cdotb \Ub + \frac{1}{(\gammabar + \delta \Gamma_1) \; p_0} 
  \Ub \cdotb \nablab p_0 = S - \frac{1}{(\gammabar + \delta \Gamma_1) \; p_0} 
  \frac{\partial p_0}{\partial t} \enskip .
\end{equation}

Assuming that $\delta \Gamma_1 \ll \gammabar$, we then have
\begin{equation}
\nablab \cdotb \Ub + \frac{1}{\gammabar p_0} \Ub \cdotb \nablab p_0 = S - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \frac{\partial p_0}{\partial t} +
\frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ub \cdotb \nablab p_0 \enskip , \label{eq:gammafull}
\end{equation}
The base state evolution equation is the average of this over a layer
\begin{equation}
\nablab \cdot w_0 \er + \frac{1}{\gammabar p_0} w_0 \er \cdotb \nablab p_0 =
\Sbar - \frac{1}{\gammabar p_0} \frac{\partial p_0}{\partial t} + \overline{
  \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \ut \cdotb \nablab p_0
  \right ) } \enskip .
\end{equation}
Subtracting this from equation (\ref{eq:gammafull}), we have
\begin{equation}
\nablab \cdotb \Ubt + \frac{1}{\gammabar p_0} \Ubt \cdotb \nablab p_0 = S -
\Sbar + \frac{\delta \Gamma_1}{\gammabar^2 p_0} \left (\psi + \Ubt \cdotb
\nablab p_0 \right ) - \overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \Ubt
\cdotb \nablab p_0 \right ) } \enskip .
\end{equation}

These can be written more compactly as:
\begin{equation}
\frac{\partial w_0}{\partial r} = \Sbar -\frac{1}{\gammabar p_0}\psi +
\overline{ \left ( \frac{\delta \Gamma_1}{\gammabar^2 p_0} \ut \cdotb \nablab
  p_0 \right ) } \enskip , \label{eq:base_w0_with_dgamma1}
\end{equation}
for plane-parallel geometries (analogous to eq. [\ref{eq:divw0}]), and
\begin{equation}
\nablab \cdotb (\beta_0 \Ubt) = \beta_0 \left [ S - \Sbar + \frac{\delta
    \Gamma_1}{\gammabar^2 p_0} \psi + \frac{\delta \Gamma_1}{\gammabar^2 p_0}
  \Ubt \cdotb \nablab p_0 - \overline{ \left ( \frac{\delta
      \Gamma_1}{\gammabar^2 p_0} \Ubt \cdotb \nablab p_0 \right ) } ~ \right ]
 \enskip ,  \label{eq:constraint_with_delta_gamma}
\end{equation}

This constraint is not in a form that can be projected.  To solve this form, we 
need to use a lagged $\Ubt$ in the righthand side.

\subsection{Thermal Diffusion Changes}
Immediately after {\bf Step 4H}, diffuse the enthalpy through 
a time interval of $\dt$.  First, define $(\rho h)^{(1a),\star} = (\rho h)^{(2),\star}$.  
We recompute $(\rho h)^{(2),\star}$ to account for thermal diffusion.  Here we begin
with the enthalpy equation, but consider only the 
diffusion terms,
\begin{equation}
\frac{\partial (\rho h)}{\partial t} = \nabla\cdot\kth\nabla T.
  \end{equation}
We can recast this as an enthalpy-diffusion equation by applying the
chain-rule to $h(p_0,T,X_k)$,
\begin{equation}
\nabla h = h_p \nabla p_0 + c_p \nabla T + \sum_k \xi_k \nabla X_k \enskip ,
\end{equation}
giving
\begin{equation}
  \frac{\partial (\rho h)}{\partial t}  = 
 \nabla\cdot \frac{\kth}{c_p}\nabla h -  
 \sum_k \nabla\cdot \frac{\xi_k \kth}{c_p}\nabla X_k -
 \nabla\cdot \frac{h_p \kth}{c_p}\nabla p_0.
  \end{equation}
Compute $\kth^{(1)}, c_p^{(1)}$, and $\xi_k^{(1)}$ from $\rho^{(1)}, T^{(1)}$, and $X_k^{(1)}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(2),\star} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2),\star}$,
\begin{eqnarray}
\left(\rho^{(2),\star} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla\right)h^{(2),\star} &=& (\rho h)^{(1a),\star} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n+1,\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{n}\right),
\end{eqnarray}
